Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-11-05 paper/main.tex
fix latex syntax
restructure quotes of anterior vs. posterior PPA

% Baldassano (2013). Differential connectivity with Parahippocampal Place Area
\citep{baldassano2013differential}, from abstract: We utilize a functional
connectivity measure for fMRI that can estimate connectivity differences at the
voxel level. We provide the first direct evidence that anterior and posterior
PPA exhibit distinct connectivity patterns. Anterior PPA is more strongly
connected to regions in the default mode network (including the parieto-medial
temporal pathway). Posterior PPA more strongly connected to occipital visual
regions.
% gradient
Object sensitivity in the PPA also has an anterior–posterior gradient, with
stronger responses to abstract objects in posterior PPA.
% summary
Results (and previous work) suggest that posterior PPA is concerned primarily
with perception of low-level visual features and object shape, while anterior
PPA is involved in memory and global contextual processing.

% from Baldassano discussion
\citep{baldassano2013differential}, from discussion: our results demonstrate
that PPA exhibits a gradient in connectivity along anterior–posterior axis
(analogous to the gradient in connectivity along macaque TH/TF/TFO). The
connectivity gradient was also paired with a functional gradient of sensitivity
to scene and abstract object stimuli. Results demonstrate that anterior and
posterior PPA connect differentially to two distinct cortical networks.
% but not independent
Data suggest that PPA might contain identifiable subregions, but subregions
should not be considered as completely independent modules. Both subregions
activate selectively to scenes, and the parahippocampal region (at least in
macaques) is densely self-connected (Suzuki, 2009), implying that these
subregions cooperate to build a complete representation of a scene. Their
distinct connectivity properties, however, suggests that each may be involved in
specific aspects of visual and cognitive processing involved in the overarching
goal of scene understanding.

% posterior PPA
Posterior PPA shows a stronger response to abstract objects than anterior PPA,
and is more strongly connected to all of occipital visual cortex, including LOC
and TOS. These regions have well-defined retinotopic maps (Arcaro et al., 2009;
Nasr et al., 2011), and are associated with the perception of low-level visual
features and object shape. Previous work has hinted that posterior PPA is more
responsive to both simple visual textures and objects; Arcaro et al. (2009)
found that a posterior portion of PPA responded about four times as strongly to
a flickering checker-board stimulus compared to an anterior portion, and that
the response to objects was greater than the response to scrambled images only
in the posterior portion => posterior PPA may be more visually responsive than
anterior PPA.
% LLA
Our description of posterior PPA is in fact similar to the original proposal of
Aguirre et al. for a “lingual landmark area” (LLA), slightly posterior to PPA,
which was “specialized for the perception of visual stimuli with orienting
value” (Aguirre et al., 1998) and carried out bottom-up perceptual analysis to
recognize locations or landmarks (Cant and Goodale, 2007; Epstein et al., 1999).
Although the LLA is no longer identified as an independent region from PPA in
current studies, it is possible that the posterior portion of PPA corresponds to
the properties of the proposed LLA, offering an explanation for why this region
was localized more posteriorly than the full PPA.

% Anterior PPA
Anterior PPA is specifically connected to RSC, cIPL, medial PFC, and the lateral
surface of the anterior temporal lobe. This portion of PPA is less visually
responsive to both scenes and objects, with notably low sensitivity to abstract
object stimuli.

% DMN
\citep{baldassano2013differential} regarding DMN: the set of regions connected
more strongly to anterior PPA is strikingly similar to the Default Mode Network
(DMN) (Buckner et al., 2008; Fox et al., 2005; Raichle et al., 2001), which is
known to include the parahippocampal region. The only portions of the DMN that
do not show differential connectivity to anterior PPA in our data are the
rostral portion of the posterior cingulate cortex (PCC) and the superior frontal
cortex.
% PPA and DMN
DMN has been implicated in a large number of internally-focused tasks, one of
its key roles involves autobiographical memory (Buckner et al., 2008). Models of
recognition memory have previously identified parahippocampal cortex as
primarily encoding spatial context information (Eichenbaum et al., 2007). Data
from Aminoff et al. (2007) has suggested that an anterior portion of PPA may be
involved in recall based on spatial context. Our results are consistent with
anterior PPA playing a more central role in memory than posterior PPA, given
anterior PPA's connectivity with the DMN.
%
The fact that anterior PPA had a lower sensitivity to our abstract object
stimuli does not necessarily imply that this region does not use object
information. Previous work has shown that PPA responds to objects that have
spatial associations (Aminoff et al., 2007), are space-defining (Mullally and
Maguire, 2011), and are navigationally-relevant (Janzen and Van Turennout,
2004). These types of responses require spatial memory and cannot be based
purely on visual features like object shape. If anterior PPA is involved in
processing spatial context, then space-defining or navigationally-relevant
objects could activate anterior PPA more strongly than our abstract objects,
which were unfamiliar and provided no sense of context or orientation. Further
experiments will be required to determine what type of object-related
information is used in this region.

@@

\tod[inline]{hypothesis of increased activation correlation with changes in the
    soundscape; cf. control contrasts (e.g. \texttt{vse\_new} >
    \texttt{pe\_old}).
% foreshadowing of narrator by soundscape
Further, verbal cues are regularly forestalled by changes of the
soundscape.
% arnott
\todo[inline]{e.g. arnott2008crinkling find increased activations of PPA to
sound made by objects}
% hypothesis
We hypothesize that not just semantic information but also the mere changes of a
soundscape that cues a listener about a setting's spatial layout of could
correlate with increased activity in the PPA.

>>>>

% Baldassano (2013). Differential connectivity with Parahippocampal Place Area
\citep{baldassano2013differential} in general: anterior and posterior PPA
exhibit distinct connectivity patterns; object sensitivity in the PPA also has
an anterior-posterior gradient; connectivity gradient was also paired with a
functional gradient of sensitivity to scene and abstract object stimuli.

% gradient
Data suggest that PPA might contain identifiable subregions, but subregions
should not be considered as completely independent modules. Both subregions
activate selectively to scenes, and the parahippocampal region (at least in
macaques) is densely self- connected (Suzuki, 2009), implying that these
subregions cooperate to build a complete representation of a scene. Their
distinct connectivity properties, however, suggests that each may be involved in
specific aspects of visual and cognitive processing involved in the overarching
goal of scene understanding.

% from Baldassano discussion
\citep{baldassano2013differential} regarding posterior PPA: posterior regions
are more functionally connected to visual processing regions; posterior PPA more
strongly connected to occipital visual regions; stronger responses to abstract
objects in posterior PPA; posterior PPA is concerned primarily with perception
of low-level visual fea- tures and object shape.

\citep{baldassano2013differential} discussion of posterior PPA: Posterior PPA
shows a stronger response to abstract objects than anterior PPA, and is more
strongly connected to all of occipital visual cortex, including LOC and TOS.
These regions have well-defined retinotopic maps (Arcaro et al., 2009; Nasr et
al., 2011), and are associated with the perception of low-level visual features
and object shape. Previous work has hinted that posterior PPA is more responsive
to both simple visual textures and objects; Arcaro et al. (2009) found that a
posterior portion of PPA responded about four times as strongly to a flickering
checker-board stimulus compared to an anterior portion, and that the response to
objects was greater than the response to scrambled images only in the posterior
portion => posterior PPA may be more visually responsive than anterior PPA. Our
description of posterior PPA is in fact similar to the original proposal of
Aguirre et al. for a “lingual landmark area” (LLA), slightly posterior to PPA,
which was “specialized for the perception of visual stimuli with orienting
value” (Aguirre et al., 1998) and carried out bottom-up perceptual analysis to
recognize locations or landmarks (Cant and Goodale, 2007; Epstein et al., 1999).
Although the LLA is no longer identified as an independent region from PPA in
current studies, it is possible that the posterior portion of PPA corresponds to
the properties of the proposed LLA, offring an explanation for why this region
was localized more posteriorly than the full PPA.

\citep{baldassano2013differential} regarding anterior PPA: anterior regions are
more functionally connected to retrosplenial complex (RSC) and parietal
cortices; anterior PPA is more strongly connected to regions in the default mode
network (including the parieto-medial temporal pathway); anterior PPA is
involved in memory and global contextual processing; anterior PPA is
specifically connected to RSC, cIPL, medial PFC, and the lateral surface of the
anterior temporal lobe. This portion of PPA is less visually responsive to both
scenes and objects, with notably low sensitivity to abstract object stimuli.

\citep{baldassano2013differential} regarding DMN: the set of regions connected
more strongly to anterior PPA is strikingly similar to the Default Mode Network
(DMN) (Buckner et al., 2008; Fox et al., 2005; Raichle et al., 2001), which is
known to include the parahippocampal region. The only portions of the DMN that
do not show differential connectivity to anterior PPA in our data are the
rostral portion of the posterior cingulate cortex (PCC) and the superior frontal
cortex.  DMN has been implicated in a large number of internally-focused tasks,
one of its key roles involves autobiographical memory (Buckner et al., 2008).
Models of recognition memory have previously identified parahippocampal cor- tex
as primarily encoding spatial context information (Eichenbaum et al., 2007).
Data from Aminoff et al. (2007) has suggested that an anterior portion of PPA
may be involved in recall based on spatial context. Our results are consistent
with anterior PPA playing a more central role in memory than posterior PPA,
given anterior PPA's connectivity with the DMN. The fact that anterior PPA had a
lower sensitivity to our abstract object stimuli does not necessarily im ply
that this region does not use object information. Previous work has shown that
PPA responds to objects that have spatial associations (Aminoff et al., 2007),
are space-defining (Mullally and Maguire, 2011), and are navigationally-
relevant (Janzen and Van Turennout, 2004). These types of responses require
spatial memory and cannot be based purely on visual features like object shape.
If anterior PPA is involved in processing spatial context, then space-defining
or navigationally-relevant objects could activate anterior PPA more strongly
than our abstract objects, which were unfamiliar and provided no sense of
context or orientation. Further experiments will be required to determine what
type of object-related information is used in this region.

@@

\todo[inline]{hypothesis of increased activation correlation with changes in the
    soundscape; cf. control contrasts (e.g. \texttt{vse\_new} >
    \texttt{pe\_old})}.
% foreshadowing of narrator by soundscape
Further, verbal cues are regularly forestalled by changes of the soundscape.
% arnott
\todo[inline]{e.g. arnott2008crinkling find increased activations of PPA to
sound made by objects}
% hypothesis
We hypothesize that not just semantic information but also the mere changes of a
soundscape that cues a listener about a setting's spatial layout of could
correlate with increased activity in the PPA.
